A UK Case Study on\\Cybersecurity Education and Accreditation

### 2019-07-24 FIE2019-final.tex
Tidying
Final tweaks to abstract

\newif\ifanon
\anontrue
\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[hyphenbreaks]{breakurl}
\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

\title{A UK Case Study on\\Cybersecurity Education and Accreditation}
%\title{Cybersecurity Education Is Too Important\\To Be Left To The Specialists} Save this for a future paper?
%\title{What Do We Mean By Cybersecurity Education?}  Tom's original

% \author{\IEEEauthorblockN{Tom Crick}
% \IEEEauthorblockA{\textit{School of Education} \\
% \textit{Swansea University}\\
% Swansea, UK \\
% thomas.crick@swansea.ac.uk}
% \and
% \IEEEauthorblockN{James H. Davenport}
% \IEEEauthorblockA{\textit{Department of Computer Science} \\
% \textit{University of Bath}\\
% Bath, UK \\
% j.h.davenport@bath.ac.uk}
% \and
% \IEEEauthorblockN{Alastair Irons}
% \IEEEauthorblockA{\textit{Faculty of Technology} \\
% \textit{name of organization (of Aff.)}\\
% Sunderland University, Sunderland, UK\\
% alastair.irons@sunderland.ac.uk}
% \and
% \IEEEauthorblockN{Tom Prickett}
% \IEEEauthorblockA{\textit{Department of Computing and Information Sciences} \\
% \textit{name of organization (of Aff.)}\\
% Northumbria University, Newcastle upon Tyne, UK \\
% tom.prickett@northumbria.ac.uk}
% }
% \ifanon
% \author{Anonymous}
% \else
% compact IEEE author format for more than three authors...
\author{\IEEEauthorblockN{Tom Crick\IEEEauthorrefmark{1}, James
    H. Davenport\IEEEauthorrefmark{2}, Alastair
    Irons\IEEEauthorrefmark{3} and Tom Prickett\IEEEauthorrefmark{4}} 
\IEEEauthorblockA{\IEEEauthorrefmark{1}%School of Education, 
Swansea University, Swansea, UK; Email: thomas.crick@swansea.ac.uk} 
\IEEEauthorblockA{\IEEEauthorrefmark{2}%Dept.~Computer Science, 
University of Bath, Bath, UK; Email: j.h.davenport@bath.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{3}%Faculty of Technology, 
Sunderland University, Sunderland, UK; Email: alastair.irons@sunderland.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{4}%Dept.~Computer\&Information Sciences, 
Northumbria University, Newcastle upon Tyne, UK; Email: tom.prickett@northumbria.ac.uk}}
%\fi
\maketitle

\begin{abstract}
% submitted abstract (100-500 word limit):
This Innovative Practice Full Paper presents a national case study-based analysis of the numerous dimensions to cybersecurity education and how they are implemented and accredited; from understanding the interaction of hardware and software, moving from theory to practice (and vice versa), to human factors, policy and politics (as well as other important facets). A multitude of model curricula and recommendations have been presented and discussed in international fora in recent years, with varying levels of impact on education, policy and practice. This paper address three key questions: {\emph{i)}} What is taught and what should be taught for cybersecurity to general computer science students; {\emph{ii)}} Should cybersecurity be taught stand-alone or in an integrated manner to general computer science students;  and {\emph{iii)}} Can accreditation by national professional, statutory and regulatory bodies enhance the provision of cybersecurity within a body's jurisdiction?

Evaluating how cybersecurity is taught in all aspects of computer science is clearly a task of considerable size, one that is beyond the scope of this paper. Instead a case study-based research approach, primarily focusing on the UK, has been adopted to evaluate the evidence of the teaching of cybersecurity within general computer science to university-level students. Thus, in the context of widespread international computer science/engineering curriculum reform, what does this need to embed cybersecurity mean more generally for institutions and educators, and how can we teach this subject more effectively? Through this UK case study, and by contrasting with the US, we demonstrate the positive effect that national accreditation requirements can have, and give some recommendations both for future research and curriculum developments.

%The paper proposes a number of recommendations for future cybersecurity educational initiatives, interventions and research, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

>>>>

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{paralist}
\usepackage{url}
\usepackage{enumitem}
\usepackage[noadjust]{cite}
\usepackage[hyphenbreaks]{breakurl}
%\usepackage[T1]{fontenc}
\usepackage{booktabs} % For formal tables

@@

\title{A UK Case Study on\\Cybersecurity Education and Accreditation}

% \author{\IEEEauthorblockN{Tom Crick}
% \IEEEauthorblockA{\textit{School of Education} \\
% \textit{Swansea University}\\
% Swansea, UK \\
% thomas.crick@swansea.ac.uk}
% \and
% \IEEEauthorblockN{James H. Davenport}
% \IEEEauthorblockA{\textit{Department of Computer Science} \\
% \textit{University of Bath}\\
% Bath, UK \\
% j.h.davenport@bath.ac.uk}
% \and
% \IEEEauthorblockN{Alastair Irons}
% \IEEEauthorblockA{\textit{Faculty of Technology} \\
% \textit{name of organization (of Aff.)}\\
% Sunderland University, Sunderland, UK\\
% alastair.irons@sunderland.ac.uk}
% \and
% \IEEEauthorblockN{Tom Prickett}
% \IEEEauthorblockA{\textit{Department of Computing and Information Sciences} \\
% \textit{name of organization (of Aff.)}\\
% Northumbria University, Newcastle upon Tyne, UK \\
% tom.prickett@northumbria.ac.uk}
% }

% compact IEEE author format for more than three authors...
\author{\IEEEauthorblockN{Tom Crick\IEEEauthorrefmark{1}, James
    H. Davenport\IEEEauthorrefmark{2}, Alastair
    Irons\IEEEauthorrefmark{3} and Tom Prickett\IEEEauthorrefmark{4}} 
\IEEEauthorblockA{\IEEEauthorrefmark{1}%School of Education, 
Swansea University, Swansea, UK; Email: thomas.crick@swansea.ac.uk} 
\IEEEauthorblockA{\IEEEauthorrefmark{2}%Dept.~Computer Science, 
University of Bath, Bath, UK; Email: j.h.davenport@bath.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{3}%Faculty of Technology, 
Sunderland University, Sunderland, UK; Email: alastair.irons@sunderland.ac.uk}
\IEEEauthorblockA{\IEEEauthorrefmark{4}%Dept.~Computer\&Information Sciences, 
Northumbria University, Newcastle upon Tyne, UK; Email: tom.prickett@northumbria.ac.uk}}

\maketitle

\begin{abstract}
This Innovative Practice Full Paper presents a national case study-based analysis of the numerous dimensions to cybersecurity education and how they are prioritised, implemented and accredited; from understanding the interaction of hardware and software, moving from theory to practice (and vice versa), to human factors, policy and politics (as well as various other important facets). A multitude of model curricula and recommendations have been presented and discussed in international fora in recent years, with varying levels of impact on education, policy and practice. This paper address three key questions: {\emph{i)}} what is taught and what should be taught for cybersecurity to general computer science students; {\emph{ii)}} should cybersecurity be taught stand-alone or in an integrated manner to general computer science students; and {\emph{iii)}} can accreditation by national professional, statutory and regulatory bodies enhance the provision of cybersecurity within a body's jurisdiction?

Evaluating how cybersecurity is taught in all aspects of computer science is clearly a task of considerable size, one that is beyond the scope of this paper. Instead a case study-based research approach -- primarily focusing on the UK -- has been adopted to evaluate the evidence of the teaching of cybersecurity within general computer science to university-level students. Thus, in the context of widespread international computer science/engineering curriculum reform, what does this need to embed cybersecurity knowledge and skills mean more generally for institutions and educators, and how can we teach this subject more effectively? Through this UK case study, and by contrasting with related initiatives in the US, we demonstrate the positive effect that national accreditation requirements can have, and offer some recommendations both for future research and curriculum developments.
\end{abstract}
